Adopting agile in the large: motivations, success factors and challenges

### 2013-10-29 journal/article.tex
Set document style to IST as an example

%\documentclass[12pt,a4paper,english,oneside]{article}
\documentclass[lnbip]{svmultln}

@@

\usepackage{calc}
\usepackage{natbib}
\usepackage{url}
\usepackage{listings}
\usepackage{hyphenat}

@@

@@

\selectlanguage{english}

\mainmatter

@@

\titlerunning{Adopting agile in the large}

\author{Kim Dikert \and Maria Paasivaara \and Casper Lassenius}
\authorrunning{Kim Dikert et al.}   % abbreviated author list (for running head)

% list of authors for the TOC (use if author list has to be modified)
\tocauthor{Kim Dikert, Maria Paasivaara, Casper Lassenius}

\institute{Aalto University, School of Science,
Department of Computer Science and Engineering
\\ \email{kim-karol.dikert@aalto.fi}, \email{maria.paasivaara@aalto.fi}, \email{casper.lassenius@aalto.fi} }

\maketitle

% ---------------------------------------------------------------------
% -------------- ABSTRACT AND TEXT ------------------------------------
% ---------------------------------------------------------------------

@@

\keywords {agile, transformation, large scale, adopting agile}
\end{abstract}

% ---------------------------------------------------------------------
\section{Introduction}

@@

@@

\begin{table}
    \begin{tabular}{ p{0.24\textwidth} l l }
        \toprule
        Database      & URL                     & N of matches   \\
        \midrule
        IEEExplore    & http://ieeexplore.ieee.org      & 745 \\ 
        ACM           & http://dl.acm.org               & 168 \\
        Scopus        & http://www.scopus.com/home.url  & 1596 \\
        Web of Knowledge\newline(Thomson Reuters) &
        http://apps.webofknowledge.com & 786 \\
        \bottomrule
    \end{tabular}
    \caption{Databases included in search}
    \label{table:databases}
\end{table}

@@

\bibliographystyle{plain}
\bibliographystylegen{plain}

>>>>

%\documentclass[12pt,a4paper,english,oneside]{article}
\documentclass[preprint,authoryear,12pt]{elsarticle}

@@

\usepackage{calc}
\usepackage{natbib}
\usepackage{url}
%\usepackage{listings}
\usepackage{hyphenat}

@@

\journal{Information and Software Technology}

@@

% Extra definitions?
\selectlanguage{english}

\begin{frontmatter}

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for the associated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for the associated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for the associated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%%
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{<author name>}
%% \address[label1]{<address>}
%% \address[label2]{<address>}

@@

\author{Kim Dikert, Maria Paasivaara, Casper Lassenius}

\address{Aalto University, School of Science, Department of Computer Science and Engineering}

\ead{kim-karol.dikert@aalto.fi, maria.paasivaara@aalto.fi, casper.lassenius@aalto.fi}

% ---------------------------------------------------------------------
% ------------------------- ABSTRACT ----------------------------------
% ---------------------------------------------------------------------

@@

\end{abstract}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)

agile \sep transformation \sep large scale \sep adopting agile

\end{keyword}

\end{frontmatter}

% ---------------------------------------------------------------------
% --------------------------- TEXT ------------------------------------
% ---------------------------------------------------------------------

\section{Introduction}

@@

Jos koko on epäselvä:
--> Tutkijat päättävät keskustelun ja kvalitatiivisen harkinnan perusteella
--> Tähän tarvitaan esimerkit, milloin on otettu mukaan, milloin on karsittu
    pois

@@

\begin{table}
    \begin{tabular}{ p{0.28\textwidth} l l }
        \toprule
        Database      & URL                     & N of matches   \\
        \midrule
        IEEExplore    & http://ieeexplore.ieee.org      & 745 \\ 
        ACM           & http://dl.acm.org               & 168 \\
        Scopus        & http://www.scopus.com/home.url  & 1596 \\
        Web of Knowledge\newline(Thomson Reuters) &
        http://apps.webofknowledge.com & 786 \\
        \bottomrule
    \end{tabular}
    \caption{Databases included in search}
    \label{table:databases}
\end{table}

@@

\bibliographystyle{elsarticle-harv}
%\bibliographystyle{plain}
\bibliographystylegen{plain}
